WASP-4 is accelerating towards the Earth

### 2019-09-11 rnaas_note/ms.tex
rnaas minor

%FoHJ: gammadot = -0.0099^{+0.0052}_{-0.0054}
The AIC and BIC strongly favored a model with a linear trend ($\Delta
{\rm BIC}=73$ compared to a model without the linear trend).
Figure~\ref{fig:rv_o_minus_c} shows the best-fitting model, with the
orbit of WASP-4b subtracted.  The best-fit radial velocity derivative,
$\dot{v}_{\rm r}$, is
\begin{equation}
  \dot{v}_{\rm r} = -0.0422^{+0.0028}_{-0.0027}\,{\rm m\,s^{-1}\,day^{-1}}.
\end{equation}
This acceleration towards our line of sight is 4.3 times faster than
the suggested $\approx 2\sigma$ trend \citet{knutson_friends_2014}
found from the shorter baseline.  The radial velocity values are
available in the data-behind-the-figure online version of this {\it
Note}.

@@

While the quantitative agreement is not perfect, Occam's razor would
suggest that the line of sight acceleration is probably a sufficient
explanation for the apparent decrease of WASP-4b's orbital period.
While further radial velocity observations of the system should help
clarify the mass and semi-major axis of the companion, it seems
unlikely that additional transit observations will yield near-term
constraints on orbital decay.

>>>>

%FoHJ: gammadot = -0.0099^{+0.0052}_{-0.0054}
The AIC and BIC strongly favored a model with a linear trend ($\Delta
{\rm BIC}=73$ compared to a model without the linear trend).
Figure~\ref{fig:rv_o_minus_c} shows the best-fitting model, with the
orbit of WASP-4b subtracted.  The best-fit radial velocity derivative,
$\dot{v}_{\rm r}$, is
\begin{equation}
  \dot{v}_{\rm r} = -0.0422^{+0.0028}_{-0.0027}\,{\rm m\,s^{-1}\,day^{-1}}.
\end{equation}
This acceleration towards our line of sight is 4.3 times faster than
the $\approx$$2\sigma$ trend \citet{knutson_friends_2014}
found from the shorter baseline.  The radial velocity values are
available in the data-behind-the-figure online version of this {\it
Note}.

@@

Though the quantitative agreement is not perfect, Occam's razor would
suggest that the line of sight acceleration is probably a sufficient
explanation for the apparent decrease of WASP-4b's orbital period.
While further radial velocity observations of the system should help
in determining the mass and semi-major axis of the companion, it seems
unlikely that additional transit observations will yield near-term
constraints on orbital decay.
